Formalizing the Kolmogorov extension Theorem in Lean

### 2023-09-18 Manuscript/proof_outline.tex
add lean ref

The goal of our contribution is a formalization of the proof of that theorem in {\tt Lean}. We are using \leanline{Lean4} and its mathematical library \leanline{mathlib} \cite{mathlib2020lean}\footnote{All references to results in \leanline{mathlib} are accurate for commit {\tt 537e7f030d6df737d728c7c002fb1928f4615afa}, August 22, 2023.}.
The Kolmogorov extension theorem is on the interface between measure theory and probability theory. Here, we rely on a decent amount of formalized mathematics in the measure-theory part of {\tt mathlib} (outer measures, above all), while not requiring any specific previous formalization of probability theory. (In fact, most of our results are formulated in terms of finite rather than probability measures.)

>>>>

The goal of our contribution is a formalization of the proof of that theorem in {\tt Lean}. We are using \leanline{Lean4}\cite{moura2021lean} and its mathematical library \leanline{mathlib} \cite{mathlib2020lean}\footnote{All references to results in \leanline{mathlib} are accurate for commit {\tt 537e7f030d6df737d728c7c002fb1928f4615afa}, August 22, 2023.}.
The Kolmogorov extension theorem is on the interface between measure theory and probability theory. Here, we rely on a decent amount of formalized mathematics in the measure-theory part of {\tt mathlib} (outer measures, above all), while not requiring any specific previous formalization of probability theory. (In fact, most of our results are formulated in terms of finite rather than probability measures.)
